On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-12-05 arity1.tex
Update arity1.tex

\subsection{$\alpha = 1$, unary}

@@

\subsubsection{$\delta = 2$\\}

@@

\subsubsection{$\delta = 3$\\}

\textbf{A.} First, let us assume that a fixed bead on a side of $\hexagon_p^n$ has a free hand, and bead $i$ binds to it. If the most stable conformation formed by beads $i, i+1, i+2$ has only two hydrogen bonds, it will be nondeterministic because there are at least two possibilities, see Fig.~\ref{fig:beadi}. Therefore, it needs to make three hydrogen bonds to deterministically stabilize $i$.\\

@@

There are the five cases in which beads $i, i+1, i+2$ can have three bonds, see Fig.~\ref{fig:3bonds}. If there are beads having a free hand at (1,0) and (-1,0), there will be at least two possibilities in Fig.~\ref{fig:beadi-1} when a bead $i-1$ is fixed at (0,0). It is nondeterministic and beads $i-1, i, i+1$ needs to make three hydrogen bonds to prevent from it. That is, it is impossible to put beads having a free hand at (-1,0), (0,0) and (1,0). It is impossible to realize (b) and (e) in Fig.~\ref{fig:3bonds}. (d) in Fig.~\ref{fig:3bonds} becomes nondeterministic when bead $i$ is fixed because bead $i$ can be fixed at (-1,0) and bond with (-2,0), bead $i+1$ can be placed (0,1) and bond with (0,0) and bead $i+2$ can be placed (1,1) and bond with (0,1). If it makes three bonds once, such as (a) and (c) in Fig.~\ref{fig:3bonds}, it will need to make three bonds forever to be deterministic. Similarly to case 1. in the previous section, (a) and (c) in Fig.~\ref{fig:3bonds} become nondeterministic finally when it reaches a first corner of $\hexagon_p^n$.

@@

      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (-1.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [above] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (-0.5, 0.866);
        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dashed] [red] (-0.5, 0.866) -- (0.0, 0.0);
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (-1.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [above] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (-0.5, 0.866);
        \draw [dashed] [red] (-1.0, 0.0) -- (0.0, 0.0);
        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
      \end{tikzpicture}

    \end{tabular}
    \caption{When a bead$i-1$ is fixed at (0,0)}
    \label{fig:beadi-1}
  \end{center}
\end{figure}

\textbf{B.} Next, let us assume that bead $i$'s predecessor at (0,0) has no free hand and that there is a bead at (1,0) which has a free hand. If there is a bead at (1,0) and beads $i, i+1, i+2$ make only two hydrogen bonds, it will become nondeterministic as in Fig.~\ref{fig:beadat(1,0)}. That is, beads $i, i+1, i+2$ need to make three bonds to stabilize $i$. If they make three hydrogen bonds, the situation is analogous to \textbf{A}. There should not be any bead having a free hand at (1,0) or (-1,0) to prevent from becoming \textbf{A}. Let us discuss the moment after bead $i$ is fixed outside $\hexagon_p^n$. Now bead $i$ has a free hand. If beads $i+1, i+2, i+3$ can form only two bonds, it will be nondeterministic because there are at least two possible such structures, as in Fig.~\ref{fig:beadi2}. Hence, they need to form three bonds to deterministically stabilize, such as in Fig.~\ref{fig:3bonds2}. (a) in Fig~\ref{fig:3bonds2} becomes \textbf{A} because it makes three hydrogen bonds. (b) in Fig.~\ref{fig:3bonds2} becomes nondeterministic when bead $i$ is fixed because bead $i$ can be fixed at (1,0).\\

@@

>>>>

\subsection{$\alpha = 1$, unary}
\label{sec:unary}

@@

\subsubsection{\ref{sec:unary}.1 \ \ $\delta = 2$\\}

@@

\subsubsection{\ref{sec:unary}.2 \ \ $\delta = 3$\\}

\begin{enumerate}
\item Let us discuss that a fixed bead on a side of $\hexagon_p^n$ has a free hand, and bead $i$ binds to it. If the most stable conformation formed by beads $i, i+1, i+2$ has only two hydrogen bonds, it will be nondeterministic because there are at least two possibilities, see Fig.~\ref{fig:beadi}. Therefore, it needs to make three hydrogen bonds to deterministically stabilize $i$.\\

@@

@@

There are the five cases in which beads $i, i+1, i+2$ can have three bonds, see Fig.~\ref{fig:3bonds}. There are beads having a free hand at (1,0) and (-1,0) to realize (b) and (e) in Fig.~\ref{fig:3bonds} before a bead $i-1$ is fixed at (0,0). One of these two beads may be a predecessor of a bead $i-1$, but at least one bead is not. A bead $i-1$ makes a hydrogen bond with one of these two beads which is not its predecessor when it is fixed at (0,0). That is, it is impossible to put three beads having a free hand at (-1,0), (0,0) and (1,0) when a bead $i$ is fixed, and then, to realize (b) and (e) in Fig.~\ref{fig:3bonds}. (d) in Fig.~\ref{fig:3bonds} becomes nondeterministic when bead $i$ is fixed because bead $i$ can be fixed at (-1,0) and bond with (-2,0), bead $i+1$ can be placed (0,1) and bond with (0,0) and bead $i+2$ can be placed (1,1) and bond with (0,1). If it makes three bonds once, such as (a) and (c) in Fig.~\ref{fig:3bonds}, it will need to make three bonds forever to be deterministic. Similarly to case 1. in the previous section, (a) and (c) in Fig.~\ref{fig:3bonds} become nondeterministic finally when it reaches a first corner of $\hexagon_p^n$.

\item Let us discuss that bead $i$'s predecessor at (0,0) has no free hand. Let us assume that there is a bead at (1,0) which has a free hand. If there is a bead at (1,0) and beads $i, i+1, i+2$ make only two hydrogen bonds, it will become nondeterministic as in Fig.~\ref{fig:beadat(1,0)}. That is, beads $i, i+1, i+2$ need to make three bonds to stabilize $i$. If they make three hydrogen bonds, the situation is analogous to (a) and (c) in Fig.~\ref{fig:3bonds}. There are not any bead having a free hand at (1,0) or (-1,0) to prevent from being (a) and (c) in Fig.~\ref{fig:3bonds}. Let us discuss the moment after bead $i$ is fixed outside $\hexagon_p^n$. Now bead $i$ has a free hand because there are no beads having a free hand at (1,0) or (-1,0). If beads $i+1, i+2, i+3$ can form only two bonds, it will be nondeterministic because there are at least two possible such conformations, as in Fig.~\ref{fig:beadi2}. Hence, they need to form three bonds to deterministically stabilize, such as in Fig.~\ref{fig:3bonds2}. (a) in Fig~\ref{fig:3bonds2} becomes (a) in Fig.~\ref{fig:3bonds}. (b) in Fig.~\ref{fig:3bonds2} becomes nondeterministic when bead $i$ is fixed because bead $i$ can be fixed at (1,0).\\

@@

\end{enumerate}

It can yield finite conformation and the length is $3n^2+n^2+1$.
